Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis

### 2020-12-03 manuscript/manuscript.Rmd
Data availability in manuscript for medrxiv

>>>>

# Data availability

The data that support the findings of this study are available on request from the corresponding author, if legal obligations under GDPR can be met. The data are not publicly available due to privacy restrictions. We will be happy to arrange to run any analytical code locally and share the results, provided the code and the results do not leak personal information.
